IN FOCUS \\ Natural history matters: how biological constraints shape diversified interactions in pollination networks

### 2016-07-28 ms_infocus.tex
Final submission.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% MS: In Focus comment paper for Journal of Animal Ecology.
%% Draft
%% April 2016
%% Revised version: 
%% Original version wordcount: 1949 words.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper,12pt]{article}
\usepackage{comment}
\usepackage{jae}
\usepackage{lscape}
\usepackage{graphicx}
%
%---------------------------------------------------------------------------------
%
\title{IN FOCUS \\ Natural history matters: how biological constraints shape diversified interactions in pollination networks}
\running{Forbidden interactions}

@@

\nwords{1949}
\ntables{0}
\nfig{2}
\nref{14}

@@

% Forbidden links background.
% Explain the biological basis of mismatch using Fig 2 and Arditti
Forbidden links represent a family of causes for not observing specific interactions when sampling diversified plant-animal interaction networks, and stem on biological causes deeply linked to the fascinating natural history details of these interactions \citep{BasJor:2014}. The raw material for phenotypic mismatches in the specific case of hawkmoth-flower interactions is the extreme variability of the two pivotal traits determining their outcomes: proboscis length and corolla/spur or nectary depth (Fig. 2) \citep{Cocucci:2009,Arditti:2012,Nilsson:1988,Miller:1997}. This variation is extensive for both the plant and pollinator partners and observable at individual, population and species levels.

Sazatornil et al. approach would be most useful for proper tests of coevolutionary hypotheses in hawkmoth/flower assemblages (and plant-animal mutualisms in general): assessing match/mismatch patterns for every possible pairwise interaction among partners within complex webs of interaction where multiple life-history attributes may contribute biological reasons for forbidden links. The morphological match hypothesis is not the only mechanism to explain patterns of hawkmoth–plant interactions, where other life-history limitations may operate generating forbidden links, e.g., phenological mismatches (for example in the case of long-distance or elevational migratory hawkmoths), constraints from foraging for oviposition sites \citep{Alarcon:2008}, energetic constraints due to balances of nectar availability/foraging costs \citep{Borrell:2005}, etc. Most importantly, this paper nicely illustrates how the fascinating natural history details of these interactions can be use to build meaningful testable models to assess the mechanisms beyond structure and function of megadiversified webs of interactions among free-living species.

@@

My work was funded by a Severo-Ochoa Excellence Grant (SEV2012-0262) from the Spanish Ministerio de Econom\'ia y Competitividad (MINECO), and RNM-5731 from the Junta de Andaluc\'ia. Andrea Cocucci generously provided material for Fig. 1 and insightful discussions on sphingids and long-tubed flowers. Comments and suggestions by Rodrigo Medel and Jeferson Vizentin-Bugoni helped to improve the manuscript.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% MS: In Focus comment paper for Journal of Animal Ecology.
%% Draft
%% April 2016
%% Revised version: 
%% Original version wordcount: 2377 words.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper,12pt]{article}
\usepackage{comment}
\usepackage{jae}
\usepackage{lscape}
\usepackage{graphicx}
%
%---------------------------------------------------------------------------------
%
\title{IN FOCUS \\ Natural history matters: how biological constraints shape diversified interactions in pollination networks}
\running{Forbidden interactions}

@@

\nwords{2377}
\ntables{0}
\nfig{2}
\nref{14}

@@

% Forbidden links background.
% Explain the biological basis of mismatch using Fig 2 and Arditti
Forbidden links represent a family of reasons for not observing specific interactions when sampling diversified plant-animal interaction networks, and stem on biological causes deeply linked to the fascinating natural history details of these interactions \citep{BasJor:2014}. They include phenological, size, microhabitat, sensory, accessibility, or any other type of mismatches between partners that explain why some pairwise interactions never occur. The raw material for phenotypic mismatches in the specific case of hawkmoth-flower interactions is the extreme variability of the two pivotal traits determining their outcomes: proboscis length and corolla/spur or nectary depth (Fig. 2) \citep{Cocucci:2009,Arditti:2012,Nilsson:1988,Miller:1997}. This variation is extensive for both the plant and pollinator partners and observable at individual, population and species levels.

Sazatornil et al. approach would be most useful for proper tests of coevolutionary hypotheses in hawkmoth/flower assemblages (and plant-animal mutualisms in general): assessing match/mismatch patterns for every possible pairwise interaction among partners within complex webs of interaction where multiple life-history attributes may contribute biological reasons for forbidden links. The morphological match hypothesis is not the only mechanism to explain patterns of hawkmoth–plant interactions, where other life-history limitations may operate generating forbidden links, e.g., phenological mismatches (for example in the case of long-distance or elevational migratory hawkmoths), constraints from foraging for oviposition sites \citep{Alarcon:2008}, energetic constraints due to balances of nectar availability/foraging costs \citep{Borrell:2005}, etc. Match--mismatch patterns are expected when we consider these interactions across geographic mosaics at different spatial scales, with hot- and cold-spots of phenotypic matching generating variable outcomes of interactions \citep{Anderson:2010,More:2012,Pauw:2009,BasJor:2014} . Most importantly, Sazatornil et al. nicely illustrate how the fascinating natural history details of these interactions can be used to build meaningful testable models to assess the mechanisms beyond structure and function of megadiversified webs of interactions among free-living species.

@@

My work was funded by a Severo-Ochoa Excellence Grant (SEV2012-0262) from the Spanish Ministerio de Econom\'ia y Competitividad (MINECO), and RNM-5731 from the Junta de Andaluc\'ia. Andrea Cocucci and Felipe Amorim generously provided photos for the graphical summary and Fig. 1 and insightful discussions on sphingids and long-tubed flowers. Comments and suggestions by Rodrigo Medel and Jeferson Vizentin-Bugoni helped to improve the manuscript.
